\bf Title here

### 2020-07-14 paper/paper.Rmd
finish notation for plots and more plots for exploring searching space

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their intial paper on projection pursuit in 1974 that "the  technique  use  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied to more general to help practitioner to unveil the black-box in randomised iteartive (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb, amsmath, mathtools, bbm}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

\begin{equation}
\left[
\begin{array}{ccccccc}
\ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +1,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1 ,\ast} \\
\ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +2,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2, \ast} \\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j-1}l_i + l, \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i + l, \ast}\\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j}l_i , \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J} l_i, \ast}\\
\hline
\ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j-1}k_i + 1} & \cdots & \ast\\
\ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +2} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +k} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j}k_i} & \cdots & \ast \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J}\text{current/target basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{matrixA}
\end{equation}

When aggregated with information of index value and other interesting parameter, it is easier to write the basis as a column vector as in Equation \ref{eq:vectorA} and the full data structure is presneted in Equation \ref{eq:data-structure}.

All the basis can also be denoted usign a single subscript by their natural ordering as $\mathbf{A}_0, \mathbf{A}_1, \cdots, \mathbf{A}_n$.

\begin{equation}
\begin{array}{cccccccc}
\bigl[\mathbf{A}_{0, \ast, \ast} & 
\mathbf{A}_{1, 1, \ast} & 
\mathbf{A}_{1,2,\ast} & 
\cdots & 
\mathbf{A}_{1,l,\ast} & 
\cdots & 
\mathbf{A}_{1,l_1, \ast}   \\ 
\mathbf{A}_{1, \ast, 1} & 
\mathbf{A}_{1, \ast, 2} & 
\cdots &
\mathbf{A}_{1, \ast, k} &
\cdots &
\mathbf{A}_{1, \ast, k_1} &
\cdots &
\mathbf{A}_{J, l_J, \ast} \bigr]
\end{array} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|cccc|ccc}
\mathbf{A} & I & j &  l  & k & n & S_{1}& \cdots & S_{p}\\
\hline
\mathbf{A}_0 & I_0 & 0 & \ast & \ast & 1 & \ast & \cdots & \ast\\
\hline
\mathbf{A}_1 & I_1 & 1 & 1 & \ast& 2 & S_{1, 1} & \cdots & S_{p, 1}\\
\mathbf{A}_2 & I_2 & 1 & 2 &\ast & 3 & S_{1, 2} & \cdots & S_{p, 2}\\
\vdots &\vdots & \vdots &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots\\
\vdots & \vdots & 1 & l_1 & \ast & \vdots & \vdots & \cdots & \vdots\\
\hline
\vdots & \vdots & 1 & \ast & 1& \vdots &\vdots & \cdots & \vdots\\
\vdots &\vdots& 1 & \ast & 2& \vdots&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\vdots &\vdots & 1 & \ast & k_1&\vdots &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}_n & I_n & J &  l_J & \ast & n & S_{1, n}& \cdots & S_{p, n}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where $n = 1+ \sum_{i = 1}^J l_i + \sum_{i = 1}^{J-1} k_i$

@@

Using the notation we defined earlier, the plot can be defined as plotting $j$ on the x-axis and the five point summary of the following groups on the y-axis:

$$\mathbbm{1}(I_{j = j^*})$$

@@

The number of interpolation points is much managable than the searching points and always shows a pattern of gradual increase in the index value. Hence a line plot with interpolating order on the x-axis will be desirable. Using notation, the x-axis is a sequence $$x = \{1, 2, \cdots, k_1, \cdots, \sum_{i=1}^Jk_i\}$$ and y-axis are the index values defined by $y = I_{x}$.

@@

#### Another example: polishing the final projection basis

@@

*Example: Polish* In principle, all the optimisation routines should result in the same output on the same problem while this may not be true in real application. This motivates the creation of a polishing search that polishes the ending basis and achieves unity on different methods.

`search_polish` takes the ending basis of a given search as the current basis and uses a brutal-force approach to sample a large number of basis (`n_sample`) in the neighbourhood, whose radius is controlled by `polish_alpha`. Among the `n_sample` basis, the one with the largest index value becomes the candidate basis. If its index value of the candidate basis is larger than that of the current basis, it becomes the current basis in the next iteration. If no basis is found to have larger index value than the current basis, the searching neighbourhood will be shrunk and the search continues. The polishing search ends when one of the four stopping criteria is satisfied:

@@

>>>>

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their intial paper on projection pursuit in 1974 that "the  technique  use  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied to more general to help practitioner to unveil the black-box in randomised iteartive (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

\begin{equation}
\left[
\begin{array}{ccccccc}
\ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1,\ast} & \mathbf{A}_{J+1,\sum_{i = 1}^{J}l_i +1 ,\ast} \\
\ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2,\ast} & \mathbf{A}_{J+1,\sum_{i = 1}^{J}l_i +2, \ast} \\
\vdots & \vdots & \vdots & \ddots & \vdots &\vdots   \\
\ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{J+1, \sum_{i = 1}^{J-1}l_i + l, \ast}  & \mathbf{A}_{J + 1, \sum_{i = 1}^{J}l_i + l, \ast}\\
\vdots & \vdots & \vdots & \ddots & \vdots &\vdots   \\
\ast & \mathbf{A}_{1, l_1-1, \ast} & \mathbf{A}_{2, l_1 + l_2-1, \ast} & \cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i -1, \ast} & \mathbf{A}_{J+1, \sum_{i = 1}^{J+1} l_i-1, \ast}\\
\mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{J, \sum_{i = 1}^{J}l_i , \ast} & \ast\\
\hline
\ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{J, \ast,\sum_{i = 1}^{J-1}k_i + 1}  & \ast\\
\ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{J, \ast, \sum_{i = 1}^{J-1}k_i +2}  & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{J, \ast, \sum_{i = 1}^{J-1}k_i +k}  & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots   & \vdots \\
\ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{J, \ast,\sum_{i = 1}^{J}k_i} & \ast \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{A^J}\text{current/target basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{eq:matrixA}
\end{equation}

When aggregated with information of index value and other interesting parameter, it is easier to write the basis as a column vector denoting by a single subscript by their natural ordering i.e. all the bases in iteration 1 along with the starting basis as shown in Equation \ref{eq:vectorA}, can be denoted as $\mathbf{A}_0, \mathbf{A}_1, \cdots, \mathbf{A}_n$ where $n = 1 + l_1 + k_1$. The full data structure can thus be presneted as in Equation \ref{eq:data-structure}.

\begin{equation}
\begin{array}{cccccccccccc}
\bigl[
\mathbf{A}_{0, \ast, \ast} & 
\mathbf{A}_{1, 1, \ast} & 
\mathbf{A}_{1,2,\ast} & 
\cdots & 
\mathbf{A}_{1,l_1, \ast}   &
\mathbf{A}_{1, \ast, 1} & 
\mathbf{A}_{1, \ast, 2} & 
\cdots &
\mathbf{A}_{1, \ast, k_1} &
\bigr]
\end{array} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|cccc|ccc}
\mathbf{A} & I & j &  l  & k & n & S_{1}& \cdots & S_{p}\\
\hline
\mathbf{A}_0 & I_0 & 0 & \ast & \ast & 1 & \ast & \cdots & \ast\\
\hline
\mathbf{A}_1 & I_1 & 1 & 1 & \ast& 2 & S_{1, 1} & \cdots & S_{1, p}\\
\mathbf{A}_2 & I_2 & 1 & 2 &\ast & 3 & S_{2, 1} & \cdots & S_{2, p}\\
\vdots &\vdots & \vdots &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots\\
\vdots & \vdots & 1 & l_1 & \ast & \vdots & \vdots & \cdots & \vdots\\
\hline
\vdots & \vdots & 1 & \ast & 1& \vdots &\vdots & \cdots & \vdots\\
\vdots &\vdots& 1 & \ast & 2& \vdots&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\vdots &\vdots & 1 & \ast & k_1&\vdots &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}_n & I_n & J &  l_J & \ast & n & S_{n, 1}& \cdots & S_{n, p}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where $n = 1 + \sum_{i = 1}^{J+1} l_i -1 + \sum_{i = 1}^{J} k_i=  \sum_{i = 1}^{J+1} l_i + \sum_{i = 1}^{J} k_i$

@@

Using the notation we defined earlier, the plot can be defined as plotting

$$x = \{1, 2, \cdots J + 1\}$$

against the five point summary of each $j^*$ on the y-axis:

$$y = \{Q_q(I_{jlk} \cdot \mathds{1} (j = x, k = \ast))\}$$

where $q$ takes one of $0, 25, 50, 75, 100$ and $Q_q(x)$ finds the qth-quantile for the vector $x$. $\mathds{1}(.)$ is the identity operator.

@@

The number of interpolation points is much managable than the searching points and always shows a pattern of gradual increase in the index value. Hence a line plot with interpolating order on the x-axis will be desirable. Using notation, the x-axis is a sequence $$x = \{1, 2, \cdots,\sum_{i=1}^Jk_i\}$$ and y-axis are the index values defined by $$y = \{I_{jlk}: k = x\}$$

@@

#### Another example: Polish

@@

In principle, all the optimisation routines should result in the same output for the same problem while this may not be true in real application. This motivates the creation of a polishing search that polishes the final basis and achieves unity on different methods.

`search_polish` takes the final basis of a given search as the current basis and uses a brutal-force approach to sample a large number of basis (`n_sample`) in the neighbourhood, whose radius is controlled by `polish_alpha`. Among the `n_sample` basis, the one with the largest index value becomes the candidate basis. If its index value of the candidate basis is larger than that of the current basis, it becomes the current basis in the next iteration. If no basis is found to have larger index value than the current basis, the searching neighbourhood will be shrunk and the search continues. The polishing search ends when one of the four stopping criteria is satisfied:

@@

Polishing points form on itself a global structure with candidate bases and output bases. If we're allowed to abuse the notation a bit, we denote $$A_{J, \ast, \sum_{i = 1}^J k_i + 1}$$ as the first polishing basis and $$A_{J, \ast, \sum_{i = 1}^J k_i + M}$$ as the last polishing basis, where $$M = \sum_i S_{i, \text{method}} \mathds{1}(\text{method} = \text{polish})$$

Then the index plot incorporating both the interpolating points and polishing points can be defined as

$$x = \{1, 2, \cdots, \sum_{i = 1}^J k_i,(\sum_{i = 1}^J k_i + 1), \cdots,  \sum_{i = 1}^J k_i + M\}$$
$$y = \{I_{jlk}: k = x\}$$

### 2020-07-14 paper/paper.tex
finish notation for plots and more plots for exploring searching space

%% load any required packages here
\usepackage{amssymb, amsmath, mathtools, bbm} \usepackage[ruled,vlined, linesnumbered]{algorithm2e}

@@

\begin{equation}
\left[
\begin{array}{ccccccc}
\ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +1,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1 ,\ast} \\
\ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +2,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2, \ast} \\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j-1}l_i + l, \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i + l, \ast}\\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j}l_i , \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J} l_i, \ast}\\
\hline
\ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j-1}k_i + 1} & \cdots & \ast\\
\ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +2} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +k} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j}k_i} & \cdots & \ast \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J}\text{current/target basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{matrixA}
\end{equation}

When aggregated with information of index value and other interesting
parameter, it is easier to write the basis as a column vector as in
Equation \ref{eq:vectorA} and the full data structure is presneted in
Equation \ref{eq:data-structure}.

All the basis can also be denoted usign a single subscript by their
natural ordering as
\(\mathbf{A}_0, \mathbf{A}_1, \cdots, \mathbf{A}_n\).

\begin{equation}
\begin{array}{cccccccc}
\bigl[\mathbf{A}_{0, \ast, \ast} & 
\mathbf{A}_{1, 1, \ast} & 
\mathbf{A}_{1,2,\ast} & 
\cdots & 
\mathbf{A}_{1,l,\ast} & 
\cdots & 
\mathbf{A}_{1,l_1, \ast}   \\ 
\mathbf{A}_{1, \ast, 1} & 
\mathbf{A}_{1, \ast, 2} & 
\cdots &
\mathbf{A}_{1, \ast, k} &
\cdots &
\mathbf{A}_{1, \ast, k_1} &
\cdots &
\mathbf{A}_{J, l_J, \ast} \bigr]
\end{array} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|cccc|ccc}
\mathbf{A} & I & j &  l  & k & n & S_{1}& \cdots & S_{p}\\
\hline
\mathbf{A}_0 & I_0 & 0 & \ast & \ast & 1 & \ast & \cdots & \ast\\
\hline
\mathbf{A}_1 & I_1 & 1 & 1 & \ast& 2 & S_{1, 1} & \cdots & S_{p, 1}\\
\mathbf{A}_2 & I_2 & 1 & 2 &\ast & 3 & S_{1, 2} & \cdots & S_{p, 2}\\
\vdots &\vdots & \vdots &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots\\
\vdots & \vdots & 1 & l_1 & \ast & \vdots & \vdots & \cdots & \vdots\\
\hline
\vdots & \vdots & 1 & \ast & 1& \vdots &\vdots & \cdots & \vdots\\
\vdots &\vdots& 1 & \ast & 2& \vdots&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\vdots &\vdots & 1 & \ast & k_1&\vdots &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}_n & I_n & J &  l_J & \ast & n & S_{1, n}& \cdots & S_{p, n}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where \(n = 1+ \sum_{i = 1}^J l_i + \sum_{i = 1}^{J-1} k_i\)

@@

Using the notation we defined earlier, the plot can be defined as
plotting \(j\) on the x-axis and the five point summary of the following
groups on the y-axis:

\[\mathbbm{1}(I_{j = j^*})\]

@@

The number of interpolation points is much managable than the searching
points and always shows a pattern of gradual increase in the index
value. Hence a line plot with interpolating order on the x-axis will be
desirable. Using notation, the x-axis is a sequence
\[x = \{1, 2, \cdots, k_1, \cdots, \sum_{i=1}^Jk_i\}\] and y-axis are
the index values defined by \(y = I_{x}\).

@@

\hypertarget{another-example-polishing-the-final-projection-basis}{%
\paragraph{Another example: polishing the final projection
basis}\label{another-example-polishing-the-final-projection-basis}}

\emph{Example: Polish} In principle, all the optimisation routines
should result in the same output on the same problem while this may not
be true in real application. This motivates the creation of a polishing
search that polishes the ending basis and achieves unity on different
methods.

\texttt{search\_polish} takes the ending basis of a given search as the
current basis and uses a brutal-force approach to sample a large number
of basis (\texttt{n\_sample}) in the neighbourhood, whose radius is
controlled by \texttt{polish\_alpha}. Among the \texttt{n\_sample}
basis, the one with the largest index value becomes the candidate basis.
If its index value of the candidate basis is larger than that of the
current basis, it becomes the current basis in the next iteration. If no
basis is found to have larger index value than the current basis, the
searching neighbourhood will be shrunk and the search continues. The
polishing search ends when one of the four stopping criteria is
satisfied:

@@

>>>>

%% load any required packages here
\usepackage{amssymb, amsmath, mathtools, dsfont} \usepackage[ruled,vlined, linesnumbered]{algorithm2e}

@@

\begin{equation}
\left[
\begin{array}{ccccccc}
\ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1,\ast} & \mathbf{A}_{J+1,\sum_{i = 1}^{J}l_i +1 ,\ast} \\
\ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2,\ast} & \mathbf{A}_{J+1,\sum_{i = 1}^{J}l_i +2, \ast} \\
\vdots & \vdots & \vdots & \ddots & \vdots &\vdots   \\
\ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{J+1, \sum_{i = 1}^{J-1}l_i + l, \ast}  & \mathbf{A}_{J + 1, \sum_{i = 1}^{J}l_i + l, \ast}\\
\vdots & \vdots & \vdots & \ddots & \vdots &\vdots   \\
\ast & \mathbf{A}_{1, l_1-1, \ast} & \mathbf{A}_{2, l_1 + l_2-1, \ast} & \cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i -1, \ast} & \mathbf{A}_{J+1, \sum_{i = 1}^{J+1} l_i-1, \ast}\\
\mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{J, \sum_{i = 1}^{J}l_i , \ast} & \ast\\
\hline
\ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{J, \ast,\sum_{i = 1}^{J-1}k_i + 1}  & \ast\\
\ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{J, \ast, \sum_{i = 1}^{J-1}k_i +2}  & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{J, \ast, \sum_{i = 1}^{J-1}k_i +k}  & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots   & \vdots \\
\ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{J, \ast,\sum_{i = 1}^{J}k_i} & \ast \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{A^J}\text{current/target basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{eq:matrixA}
\end{equation}

When aggregated with information of index value and other interesting
parameter, it is easier to write the basis as a column vector denoting
by a single subscript by their natural ordering i.e.~all the bases in
iteration 1 along with the starting basis as shown in Equation
\ref{eq:vectorA}, can be denoted as
\(\mathbf{A}_0, \mathbf{A}_1, \cdots, \mathbf{A}_n\) where
\(n = 1 + l_1 + k_1\). The full data structure can thus be presneted as
in Equation \ref{eq:data-structure}.

\begin{equation}
\begin{array}{cccccccccccc}
\bigl[
\mathbf{A}_{0, \ast, \ast} & 
\mathbf{A}_{1, 1, \ast} & 
\mathbf{A}_{1,2,\ast} & 
\cdots & 
\mathbf{A}_{1,l_1, \ast}   &
\mathbf{A}_{1, \ast, 1} & 
\mathbf{A}_{1, \ast, 2} & 
\cdots &
\mathbf{A}_{1, \ast, k_1} &
\bigr]
\end{array} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|cccc|ccc}
\mathbf{A} & I & j &  l  & k & n & S_{1}& \cdots & S_{p}\\
\hline
\mathbf{A}_0 & I_0 & 0 & \ast & \ast & 1 & \ast & \cdots & \ast\\
\hline
\mathbf{A}_1 & I_1 & 1 & 1 & \ast& 2 & S_{1, 1} & \cdots & S_{1, p}\\
\mathbf{A}_2 & I_2 & 1 & 2 &\ast & 3 & S_{2, 1} & \cdots & S_{2, p}\\
\vdots &\vdots & \vdots &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots\\
\vdots & \vdots & 1 & l_1 & \ast & \vdots & \vdots & \cdots & \vdots\\
\hline
\vdots & \vdots & 1 & \ast & 1& \vdots &\vdots & \cdots & \vdots\\
\vdots &\vdots& 1 & \ast & 2& \vdots&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\vdots &\vdots & 1 & \ast & k_1&\vdots &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}_n & I_n & J &  l_J & \ast & n & S_{n, 1}& \cdots & S_{n, p}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where
\(n = 1 + \sum_{i = 1}^{J+1} l_i -1 + \sum_{i = 1}^{J} k_i= \sum_{i = 1}^{J+1} l_i + \sum_{i = 1}^{J} k_i\)

@@

Using the notation we defined earlier, the plot can be defined as
plotting

\[x = \{1, 2, \cdots J + 1\}\]

against the five point summary of each \(j^*\) on the y-axis:

\[y = \{Q_q(I_{jlk} \cdot \mathds{1} (j = x, k = \ast))\}\]

where \(q\) takes one of \(0, 25, 50, 75, 100\) and \(Q_q(x)\) finds the
qth-quantile for the vector \(x\). \(\mathds{1}(.)\) is the identity
operator.

@@

The number of interpolation points is much managable than the searching
points and always shows a pattern of gradual increase in the index
value. Hence a line plot with interpolating order on the x-axis will be
desirable. Using notation, the x-axis is a sequence
\[x = \{1, 2, \cdots,\sum_{i=1}^Jk_i\}\] and y-axis are the index values
defined by \[y = \{I_{jlk}: k = x\}\]

@@

\hypertarget{another-example-polish}{%
\paragraph{Another example: Polish}\label{another-example-polish}}

In principle, all the optimisation routines should result in the same
output for the same problem while this may not be true in real
application. This motivates the creation of a polishing search that
polishes the final basis and achieves unity on different methods.

\texttt{search\_polish} takes the final basis of a given search as the
current basis and uses a brutal-force approach to sample a large number
of basis (\texttt{n\_sample}) in the neighbourhood, whose radius is
controlled by \texttt{polish\_alpha}. Among the \texttt{n\_sample}
basis, the one with the largest index value becomes the candidate basis.
If its index value of the candidate basis is larger than that of the
current basis, it becomes the current basis in the next iteration. If no
basis is found to have larger index value than the current basis, the
searching neighbourhood will be shrunk and the search continues. The
polishing search ends when one of the four stopping criteria is
satisfied:

@@

Polishing points form on itself a global structure with candidate bases
and output bases. If we're allowed to abuse the notation a bit, we
denote \[A_{J, \ast, \sum_{i = 1}^J k_i + 1}\] as the first polishing
basis and \[A_{J, \ast, \sum_{i = 1}^J k_i + M}\] as the last polishing
basis, where
\[M = \sum_i S_{i, \text{method}} \mathds{1}(\text{method} = \text{polish})\]

Then the index plot incorporating both the interpolating points and
polishing points can be defined as

\[x = \{1, 2, \cdots, \sum_{i = 1}^J k_i,(\sum_{i = 1}^J k_i + 1) \cdots,  \sum_{i = 1}^J k_i + M\}\]
\[y = \{I_{jlk}: k = x\}\]
